Parsing Postfix log files

### 2009-03-02 doc/logparser-background.tex
Updated full run database.
Corrections, improvements, and new content in architecture chapter. Added SGAI and Elsevier entries to bibliography. Some minor cleanup elsewhere.
Dealt with some XXX items. Integrated some more content from the paper in the introduction section.
Some minor formatting fixes. Documented some of 'make check'. Added check for sentences with only one space separating them.

XXX db.full-run.sq3 NEEDS TO BE UPDATED AND EVERYTHING REBUILT\@.

@@

\begin{verbatim}
220 smtp.example.com ESMTP
HELO client.example.com
250 smtp.example.com
MAIL FROM: Alice N. Other alice@example.com
501 5.1.7 Bad sender address syntax
RCPT TO: Bob in Sales/Marketing bob@example.com
503 5.5.1 Error: need MAIL command
DATA
503 5.5.1 Error: need RCPT command
Message headers and body sent here.
.
502 5.5.2 Error: command not recognized
QUIT
221 2.0.0 Bye
\end{verbatim}

@@

        XXX SHOULD I URLS OR BIBLIOGRAPHY ENTRIES\@?  SHOULD I SCRAP ALL
        THE URLS AND MOVE EVERYTHING INTO THE BIBLIOGRAPHY\@?  ASK CARL\@.

>>>>

@@

\begin{verbatim}
220 smtp.example.com ESMTP
HELO client.example.com
250 smtp.example.com
MAIL FROM: Alice in Distribution alice@example.com
501 5.1.7 Bad sender address syntax
RCPT TO: Bob in Sales/Marketing bob@example.com
503 5.5.1 Error: need MAIL command
DATA
503 5.5.1 Error: need RCPT command
Message headers and body sent here.
.
502 5.5.2 Error: command not recognized
QUIT
221 2.0.0 Bye
\end{verbatim}

@@
